Resource-ratio theory in metaecosystems

### 2013-11-05 ms_resource_ratio.tex
Small fix to model description

%-----------------%
\begin{equation}
	\label{e:bnet}
	G_{i}=MIN\{\frac{g_{ij}(N_{j})}{q_{ij}}\}
\end{equation}
%-----------------%

@@

%-----------------%
\begin{equation}
	\label{e:bnet}
	\frac{dN_{jx}}{dt}=S_{jx}-eN_{jx}-\sum_{i=1}^{s}q_{ij}G_{ix}N_{jx}+\sum_{i=1}^{s}r(1-\phi)q_{ij}D_{ix}-\Delta_{Nx}
\end{equation}
%-----------------%

The inorganic nutrients are supplied to each locality via mineral alteration and atmospheric depositions at rate $S_{jx}$, and leached out of the system at rate $e$. A fraction $\phi$ of the inorganic mineral is loss out of the system during the mineralization process.

>>>>

%-----------------%
\begin{equation}
	\label{e:bnet}
	G_{ix}=MIN\{\frac{g_{ij}(N_{jx})}{q_{ij}}\}
\end{equation}
%-----------------%

@@

%-----------------%
\begin{equation}
	\label{e:bnet}
	\frac{dN_{jx}}{dt}=S_{jx}-eN_{jx}-\sum_{i=1}^{s}q_{ij}G_{ix}P_{ix}+\sum_{i=1}^{s}r(1-\phi)q_{ij}D_{ix}-\Delta_{Nx}
\end{equation}
%-----------------%

The inorganic nutrients are supplied to each locality via mineral alteration and atmospheric depositions at rate $S_{jx}$, and leached out of the system at rate $e$. A fraction $\phi$ of the inorganic nutrient contained in the detritus is lost out of the system during the mineralization process.
